Data-Driven Multi-Grid Solver for Accelerated \\ Pressure Projection

### 2022-04-06 tex/article.tex

The parameterized smoother is optimized for a set of training data $X=\{A,r^0\}$. The loss is defined as the reduction in the log-$L_2$-norm of the residual after each V-cycle iteration 
$$L = \log_{10}(|r^{k+1}|_2 / |r^{k}|_2)$$
This loss is averaged over each iteration and each example in the data-set. \textcolor{blue}{Working directly with a residual loss has a number of advantages. First and foremost, the purpose of the pressure projection step is to drive the velocity-divergence residual to zero, making this the ultimate judge of any projection method. Second, this incorporates problem-specific residual data which would be missing from a metric based only on the V-cycle operator. Finally, the residual is always available, unlike the error with respect to the unknown exact pressure solution.}

@@

The 2D and 3D dipole cases are generated using a localized residual function
$$ r_i = \hat m \cdot \left(\vec q_i-\vec Q\right)\ e^{-\sigma^2 |\vec q_i-\vec Q|^2} $$
where $\vec Q$ is a random location in the fluid domain and $\sigma$ is a random width. The same uniform $A$ matrix is used as in the static case.

>>>>

The parameterized smoother is optimized for a set of training data $X=\{A,r^0\}$. The loss is defined as the reduction in the log-$L_2$-norm of the residual after each V-cycle iteration 
\begin{equation}
L = \log_{10}(|r^{k+1}|_2 / |r^{k}|_2)
\end{equation}
This loss is averaged over each iteration and each example in the data-set. \textcolor{blue}{Working directly with a residual loss has a number of advantages. First and foremost, the purpose of the pressure projection step is to drive the velocity-divergence residual to zero, making this the ultimate judge of any projection method. Second, this incorporates problem-specific residual data which would be missing from a metric based only on the V-cycle operator. Finally, the residual is always available, unlike the error with respect to the unknown exact pressure solution.}

@@

The 2D and 3D dipole cases are generated using a localized residual function
$$ r_i = \hat m \cdot \left(\vec q_i-\vec Q\right)\ e^{-\frac{|\vec q_i-\vec Q|^2}{\sigma^2 }} $$
where $\vec Q$ is a random location in the fluid domain and $\sigma$ is a random width. The same uniform $A$ matrix is used as in the static case.
